Constraining the Interiors of Asteroids Through Close Encounters

### 2022-05-06 paper/main.tex
Apophis cadence staged

\begin{figure*}
  \centering
  \includegraphics[width=0.33\textwidth]{figs/asym-ell-likelihood.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/asym-ell-harmonic.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/asym-ell-lumpy.pdf}

  \includegraphics[width=0.33\textwidth]{figs/asym-ell-diff-likelihood.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/asym-ell-diff-harmonic.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/asym-ell-diff-lumpy.pdf}

  \includegraphics[width=0.33\textwidth]{figs/asym-ell-unc-likelihood.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/asym-ell-unc-harmonic.pdf}\hfill\hspace{0.33\textwidth}

  \includegraphics[width=0.33\textwidth]{figs/asym-ell-rat-likelihood.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/asym-ell-rat-harmonic.pdf}\hfill\hspace{0.33\textwidth}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.33\textwidth]{figs/blob-likelihood.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/blob-harmonic.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/blob-lumpy.pdf}

  \includegraphics[width=0.33\textwidth]{figs/blob-diff-likelihood.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/blob-diff-harmonic.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/blob-diff-lumpy.pdf}

  \includegraphics[width=0.33\textwidth]{figs/blob-unc-likelihood.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/blob-unc-harmonic.pdf}\hfill\hspace{0.33\textwidth}

  \includegraphics[width=0.33\textwidth]{figs/blob-rat-likelihood.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/blob-rat-harmonic.pdf}\hfill\hspace{0.33\textwidth}

@@

In figure \ref{fig:scan-space-sigma}, we show the 1$\sigma$ posterior uncertainties as a function of $K_{20}$ and $K_{22}$, or alternatively $a/c$ and $b/c$. We use axis ratios rather than the values of $a$, $b$, and $c$ to remove the $a_\mathcal{A}$ dependence of equation \ref{eqn:ellipsoid-axes}. The figure shows large uncertainty in $\gamma_0$ for $K_{22}=0$, or $a/c=b/c$, because $K_{20}$ is rotationally symmetric around $\unit z$, and $\gamma_0$ is the initial orientation with respect to the $\unit z$ axis. The system then has no dependence on $\gamma_0$ when $K_{22}=0$. This induces degeneracy in the model which inflates uncertainties, not only in $\gamma_0$ but also the other components.

@@

\jtd{More info}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.33\textwidth]{figs/asym-sph-likelihood.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/asym-sph-harmonic.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/asym-sph-lumpy.pdf}

  \includegraphics[width=0.33\textwidth]{figs/asym-sph-unc-likelihood.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/asym-sph-unc-harmonic.pdf}\hfill
  \hspace{0.33\textwidth}

@@

\jtd{The failure of this model (which is not yet reflected in the text well) makes me think we really should only do the finite element analysis. Though it is slow.}

@@

        \includegraphics[width=0.33\linewidth]{figs/out-rat-likelihood.pdf}\hfill
        \includegraphics[width=0.33\linewidth]{figs/out-rat-harmonic.pdf}\hfill
        \hspace{0.33\linewidth}
      \end{subfigure}
    \caption{Density distributions extracted for non-uniform-density asteroids with mass concentrated in the middle (\textit{left}) and the edges (\textit{right}). Within each half-figure, the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models are used. Density is normalized so that mean density is one. The same distance scale is used in all figures. The extracted distributions agree qualitatively with the true distributions. \jtd{Summarizing sentence}}
    \label{fig:non-uniform-density}
  \end{figure}
  \end{landscape}
}

For these non-uniform asteroids, the likelihood and harmonic model do not coincide, as can be seen by comparing the density distributions and that $\Delta K_{\ell m}^2$ is much larger for the harmonic distribution (indicating that the true density distribution is not harmonic). However, the two models give qualitatively similar results in that the centre-weighted density distribution contains more mass in the centre of the asteroid shape for both the harmonic and likelihood models while the edge-weighted asteroid contains mass at the edges. Though these general trends in mass placement arrived at by both the likelihood and harmonic models are accurate, the actual density distributions are inaccurate because they predict negative densities. The difference of the model output from the true distribution is generally less than $2\sigma$, but can rise to $3\sigma$ in some regions.

Figure \ref{fig:non-uniform-density} shows that the lumpy model places one large lump of greater density than the surrounding medium for the centre-weighted asteroid and less density for the edge-weighted asteroid, as expected. Greater error is incurred in $\Delta K_{\ell m}^2$ in this lumpy model than for the harmonic and likelihood models due to the lumpy model's crudeness, but the lump gives a good qualitative description of the density distribution of the asteroid which is useful for interpreting the other two models. This fact demonstrates that it can be illustrative to run the models with reduced degrees of freedom for the sake of simplicity, even if doing so yields less accurate distributions.

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=0.3\textwidth]{figs/asym-ell-likelihood.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/asym-ell-harmonic.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/asym-ell-lumpy.pdf}

  \includegraphics[width=0.3\textwidth]{figs/asym-ell-diff-likelihood.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/asym-ell-diff-harmonic.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/asym-ell-diff-lumpy.pdf}

  \includegraphics[width=0.3\textwidth]{figs/asym-ell-unc-likelihood.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/asym-ell-unc-harmonic.pdf}\hfill\hspace{0.3\textwidth}

  \includegraphics[width=0.3\textwidth]{figs/asym-ell-rat-likelihood.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/asym-ell-rat-harmonic.pdf}\hfill\hspace{0.3\textwidth}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.3\textwidth]{figs/blob-likelihood.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/blob-harmonic.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/blob-lumpy.pdf}

  \includegraphics[width=0.3\textwidth]{figs/blob-diff-likelihood.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/blob-diff-harmonic.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/blob-diff-lumpy.pdf}

  \includegraphics[width=0.3\textwidth]{figs/blob-unc-likelihood.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/blob-unc-harmonic.pdf}\hfill\hspace{0.3\textwidth}

  \includegraphics[width=0.3\textwidth]{figs/blob-rat-likelihood.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/blob-rat-harmonic.pdf}\hfill\hspace{0.3\textwidth}

@@

In figure \ref{fig:scan-space-sigma}, we show the 1$\sigma$ posterior uncertainties as a function of $K_{20}$ and $K_{22}$, or alternatively $a/c$ and $b/c$. We use axis ratios rather than the values of $a$, $b$, and $c$ because axis ratios are independent of $a_\mathcal{A}$. \jtd{The large $|K_{22}|$ sides of the $K_{2m}$-space plots correspond to asymmetric ellipsoids, as do the points far from the $a/c=b/c$ diagonal of the axis-ratio-space plots. The point corresponding to a sphere, which experiences no tidal torque and no tumbling, is at $K_{2m}=0$ and $a/c=b/c=1$.}

The figure shows large uncertainty in $\gamma_0$ for $K_{22}=0$, or $a/c=b/c$, because $K_{20}$ is rotationally symmetric around $\unit z$, and $\gamma_0$ is the initial orientation with respect to the $\unit z$ axis. The system then has no dependence on $\gamma_0$ when $K_{22}=0$. This induces degeneracy in the model which inflates uncertainties, not only in $\gamma_0$ but also the other components.

@@

\jtd{The fact that $K_{\ell m}$ are correlated indicates that, in order to correctly propagate density moment uncertainties to a density distribution, a full PPD is necessary. If only 1$\sigma$ uncertainty intervals for each parameter were used, density distribution uncertainty would be overestimated. This full PPD is produced by our fit process, but only the 1$\sigma$ uncertainties are displayed in this paper in most cases.}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.3\textwidth]{figs/asym-sph-likelihood.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/asym-sph-harmonic.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/asym-sph-lumpy.pdf}

  \includegraphics[width=0.3\textwidth]{figs/asym-sph-unc-likelihood.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/asym-sph-unc-harmonic.pdf}\hfill
  \hspace{0.3\textwidth}

@@

\jtd{The failure of this model makes me think we really should only do the finite element analysis. Though it is slow.}

For these non-uniform asteroids, the likelihood and harmonic model do not coincide, as can be seen by comparing the density distributions and that $\chi_r^2$ is much larger for the harmonic distribution (indicating that the true density distribution is not harmonic). However, the two models give qualitatively similar results in that the centre-weighted density distribution contains more mass in the centre of the asteroid shape for both the harmonic and likelihood models while the edge-weighted asteroid contains mass at the edges. Though these general trends in mass placement arrived at by both the likelihood and harmonic models are accurate, the actual density distributions are inaccurate because they predict negative densities. The difference of the model output from the true distribution is generally less than $1-1.5\sigma$ for 95\% of the asteroid. However, there are regions with very large uncertainty (as much as 14 times the local density). This leads to deviations from the local density by factors of a much as 4. The locations of these high-uncertainty regions correspond to low-density, in that they occur at the edge of the edge-weighted asteroid and at the center of the center-weighted asteroid.

Figure \ref{fig:non-uniform-density} shows that the lumpy model places one large lump of greater density than the surrounding medium for the centre-weighted asteroid and less density for the edge-weighted asteroid, as expected. Greater error is incurred in $\chi^2_r$ in this lumpy model than for the harmonic and likelihood models due to the lumpy model's crudeness, but the lump gives a good qualitative description of the density distribution of the asteroid which is useful for interpreting the other two models. This fact demonstrates that it can be illustrative to run the models with reduced degrees of freedom for the sake of simplicity, even if doing so yields less accurate distributions.

@@

        \includegraphics[width=0.33\linewidth]{figs/out-rat-likelihood.pdf}\hfill
        \includegraphics[width=0.33\linewidth]{figs/out-rat-harmonic.pdf}\hfill
        \hspace{0.33\linewidth}
      \end{subfigure}
    \caption{Density distributions extracted for non-uniform-density asteroids with mass concentrated in the middle (\textit{left}) and the edges (\textit{right}). Within each half-figure, the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models are used. Density is normalized so that mean density is one. The same distance scale is used in all figures. The extracted distributions agree qualitatively with the true distributions, but are highly uncertain and can misestimate the local density by factors of almost 4.}
    \label{fig:non-uniform-density}
  \end{figure}
  \end{landscape}
}
